formula1

### 2020-05-18 inst/formula1.Rmd
slight changes, now works

for(i in seq_len(ncol(f2017)-1)){
	y <- f2017[,i]
	if(any(y %in% noscore)){y[y%in%noscore] <- 0}
	y <- as.numeric(levels(y)[y])
	names(y) <- rownames(f2017)
	HP <- HP + pwa(ordervec2supp(y),details$pole[i],"pole")
} # i loop closes
head(HP)
(mHP <- maxp(HP))
pie(mHP)
```

@@

```{r,profsupcalc,cache=TRUE}
p <- seq(from=0.5,to=0.96,len=20)
pnames(HP)
u <- profsupp(HP,"Ricciardo",p,n=1)
u
plot(p,u-max(u))
```

>>>>

for(i in seq_len(ncol(f2017)-1)){
	y <- f2017[,i]
	if(any(y %in% noscore)){y[y%in%noscore] <- 0}
	y <- as.numeric(y)
	names(y) <- rownames(f2017)
	HP <- HP + pwa(ordervec2supp(y),details$pole[i],"pole")
} # i loop closes
head(HP)
(mHP <- maxp(HP))
pie(mHP)
loglik(indep(mHP),HP)
```

@@

```{r,profsupcalc,cache=TRUE}
p <- seq(from=0.15,to=0.25,len=10)
u <- profsupp(HP,"pole",p,n=27)
u
plot(p,u-max(u))
```
